---
title: "Developing Data Products - Week 4 Course Project"
author: "Ishmael Roslan"
date: "`r Sys.Date()`"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(palmerpenguins)
library(tidyverse)
```

## Introduction

The [palmerpenguins dataset](https://allisonhorst.github.io/palmerpenguins/) contains information
on three different penguin species. I will create two predictive models (random forest and decision tree)
to predict the species of a penguin based on input of the following variables;

 - Island
 - Bill Length
 - Bill Depth
 - Flipper Length
 - Body Mass
 - Sex
 - Year

## Looking at the Data

There are 344 penguins mentioned in the data set, 11 of which have missing data, and will therefore
be dropped from the dataset before creating models.

```{r summary}
summary(penguins)
```

## An interactive plot

The plot below shows that even using 4 of the 7 predictors, good predictive models should be obtainable.

```{r echo = FALSE}
library(palmerpenguins)
library(tidyverse)
data(penguins)
penguin_df <- 
  penguins %>%
  drop_na(sex)
library(plotly)
p <- ggplot(data = penguin_df, aes(x= bill_length_mm, y = flipper_length_mm)) +
  geom_point(aes(color = species, shape =  sex), alpha = 0.7) +
  labs(title = "Classification of Penguins",
       subtitle = "dataset: palmerpenguins",
       x = "bill length (mm)",
       y = "flipper length (mm)") +
  theme_bw()
ggplotly(p)
```


## Links

 - full source code available at [Github](https://github.com/IshmaelRoslan/DDP/tree/main/shinyPenguins)

 - fullscreen app available at [https://ishmaelroslan.shinyapps.io/shinyPenguins/](https://ishmaelroslan.shinyapps.io/shinyPenguins/)



